---
title: "Epi590 Final Project"
author: "Rebekah Hafen"
format: html
editor: visual
echo: false
warning: false
message: false
---

**About the data:** These data are from the Duke University Cardiovascular Disease Databank. This data set contains 3504 patients were referred to the university Medical Center for chest pain and were assessed with cardiac catheterization. This is performed to diagnose and open blockages in these arteries. At catheterization, a reduction of at least 75% in the artery diameter is considered a significant reduction in blood flow

```{r}
library(tidyverse)
library(gtsummary)
load(here :: here("data", "cath.rda"), verbose = TRUE)
```

```{r}
#| label: tbl-descr
#| tbl-cap: "Descriptive statistics"
table1 <- tbl_summary(
	cath,
	by = sex) |>
	add_overall(col_label= "**Total**")
table1
```

A greater proportion of male (`r inline_text(table1, variable= "sigdz", column= "stat_1")`) than female (`r inline_text(table1, variable= "sigdz", column= "stat_2")`) participants had significant coronary disease.

```{r}
#| label: tbl-two
#| tbl-cap: "Logistic regression results"
logistic_model <- glm(sigdz ~ sex + age + cad_dur + choleste,
											data = cath, family = binomial())
tbl_regression(
	logistic_model, 
	exponentiate = TRUE
)
```

```{r}
#| label: fig-hist
#| fig-cap: "Histogram of cholesterol levels (mg%)"
hist(cath$choleste)
```
